Sperm should evolve to make female meiosis fair

### 2014-05-21 writeup_and_notes/pnasSubmission/PNASSubmission.TEX
changed PNAS files to [hopefully] comply with instructions

%\abbreviations{SAM, self-assembled monolayer; OTS, octadecyltrichlorosilane}

@@

It is therefore somewhat surprising that despite the intense evolutionary pressure on female meiosis to prevent meiotic drive, 
it is potentially open to sabotage by a virtual stranger -- a haploid sperm genome.
That is, in many animal species, female meiosis is completed only after fertilization \cite{Masui_book}, 
	creating ample opportunity for interaction between the sperm and
	female meiotic machinery (note that the alternation of generations in
	likely precludes this interaction in plants). 
Therefore, a `green-bearded' \cite{Gardner2010} sperm-acting allele that recognizes and facilitates the meiotic drive of a genetically equivalent allele in heterozygous females %female meiosis %(a  heteromorphic dyad), 
     could presumably rapidly spread through a population. 
At first sight, female meiosis appears primed for exploitation by such selfish systems.  
Why then is the requirement of fertilization to complete female meiosis so ubiquitous?

@@

\section{Results}
\subsection{Invasion of an allele that promotes its own drive}
In the standard single-locus, biallelic model of female meiotic drive,
the driving allele is transmitted to the egg in heterozygotes with
probability  $d > 1/2$, regardless of sperm genotype (e.g. \cite{Ubeda2004} and see Model 1 in the Appendix for more details). 
To depict a case of a self-promoting meiotic driver,  we modify this standard model such 
	that the driver is only effective when fertilized by a sperm carrying that allele (see Figure 1A and Model 2 	in the Appendix and Supplementary Worksheet). 
We then identify the conditions allowing for the spread of this self-promoting driver, 
	and evaluate whether a driver of this form could generate a sustained conflict favoring the evolution of suppressors. 
We conclude our single locus results with an analysis of a related model (Model 3) - in which
drivers influence their transmission in females via paternal genotype,
rather than sperm haplotype.

@@

When a self-promoting driver does spread, 
	it spends much time at low frequency, 
	because the paucity of complimentary sperm compromises its ability to drive. 
However, once relatively common, it  rapidly achieves fixation due to its
	positive frequency dependent behavior (Figure 1B.1).  
The positive frequency dependence of a self-promoting driver can also
	induce bistability in its spread -- some values of $s$ 
	allow the fixation of this driver when common, but 
	preclude its invasion when rare (Equation \ref{ineqA} and Figure 1B). 
In this case, the driver will be fixed if it reaches a frequency greater than some threshold 
	(approximated in Equation \ref{bistab_homozy_approx} and  presented exactly in 
	Figure S1) and lost otherwise. 
For most parameters, this threshold is likely too high to be reached by drift, 
	and therefore  the fate of self-promoting drivers is determined
	by the more restrictive invasion criteria rather than the fixation criteria.

@@

\subsection{Two locus models of sperm-dependent female drive}
Models 2 and 3, above, explored the dynamics of an allele that drove in females when signaled by a complementary signal in sperm.   
We complement this single-locus approach %of an allele with pleiotropic effects in both sexes, 
	with alternative models of two loci - one a female driver, 
	and the other, a sperm-acting allele which modifies the effect of drive upon fertilization. 
In this model, a female meiotic driver with no sperm-dependency 
	initially reaches drive-viability equilibrium (with two alleles
	$A$ and $B$ are the ancestral non-driver and driver alleles, Figure 2A1). 
Subsequently, a sperm-acting modifier of female meiotic drive arises at another locus.

@@

%%%sperm-acting facilitator
When the modifier of drive is tightly linked to the driver and
enhances drive (i.e. in coupling phase), 
	we label  this non-recombining drive/modifier haplotype as the $B^+$ allele.  
The $B^+$ allele acts in sperm to increase the effectiveness of drive for both
	the $B$ and  $B^{+}$ alleles in $AB$ and $AB^{+}$ heterozygotes (see Figure 2A2, and Model 4 in the Appendix and Supplementary Worksheet). 
Naively, $B^{+}$ may spread by capitalizing on the additional drive it causes; however,  
	this is not the case for a few simple reasons. 
First, the novel $B^{+}$ haplotype
	arises when the ancestral driver 
	is at drive-selection balance, 
	and therefore immediately suffers a homozygous fitness cost.  
Worse yet, a novel $B^{+}$ haplotype most often helps 
	the $B$  allele drive ($B^+$ sperm meeting $AB$ eggs), because $B$ is initially more common than $B^{+}$. 
Therefore, sperm-acting drive facilitator alleles experience a profound disadvantage 
	in this scenario, even more so than under the previous two allele model. 
We have found no parameter range of this
	three allele system that allows the sperm-acting drive facilitator $B^{+}$ to
	invade the population (Appendix Model 4, Equation \eqref{coupling}, and Mathematical Supplement).

@@

\section{Appendix}
We highlight simple analytical results from: 
	the standard model of female meiotic drive (Model 1); a sperm-dependent 
	model of female meiotic drive (Model 2); a male-genotype-dependent model of
	female meiotic drive (Model 3); and more complex two-locus sperm-dependent drive models (Models 4-6). 
All models include a biallelic locus ($A/B$) with non-driving and driving alleles in frequencies $f_A$ and $f_B$, 
	respectively, while more complex models include more loci and/or alleles.  
Transmission rules describing the outcomes of all matings in each
	model are presented in a Supplementary Worksheet. 
The fitness of genotype, $g$ is sex-independent and equals $1$, $1-h_s$, and $1-s$ for genotypes $AA$, $AB$, and $BB$, respectively. 
Genotypic frequencies  equal  $f_g$ for adults in the current generation, 
	$f_g'$ in the next generation of zygotes (i.e. after recombination, random mating, drive, and syngamy, but before selection)
	and $f_g''$ in adults after selection. 
After a complete generation $f_g'' = f_g' w_g/\bar{w}$, where $\bar{w}$ is the population mean fitness and equals $\Sigma w_g f_g'$. 
Because many of our analyses assume genotype frequencies expected under Hardy Weinberg Equilibrium (HWE), we note which analytical results are approximations. 
We verify these approximations with exact numerical iterations in Supplementary Figures and Supplementary Scripts, and detail the derivation of these approximations in our Mathematical Supplement.

@@

\paragraph{Recessive fitness cost of self-promoting driver -- }
When fully recessive, the change in frequency of the self-promoting driver across generations equals 
\begin{equation}
\Delta f_B=\frac{f_A f_B^2}{\bar{w}} \left( \left(1-F\right)\left( d\left(1-2 f_A s\right) - f_B s-\frac{1}{2}\right) - s  F \right)
\label{deltadriver}
\end{equation}
where $F$ is the deviation from genotypic frequencies expected under Hardy-Weinberg. 
Assuming HWE  ($F=0$) a common, recessive, self-promoting driver invades if $s\lessapprox(2 d - 1)/(4 d)$, and fixes if
 $s\lessapprox(2d-1)/2$. 
 Therefore, when 
\begin{equation}
(2 d - 1)/(4 d)  \lessapprox  s  \lessapprox  (2d-1)/2\label{ineqA}
\end{equation} 
a recessive, self-promoting driver will deterministically fix if drift,
 	mutation, or migration pressure bring its frequency above
\begin{equation} 
f^*_{B\text{ recessive}} \approx (1-2d+4ds)/(2s(2d-1)) \label{bistab_homozy_approx}
\end{equation}
 but it will be lost when introduced below this frequency. 
 Compared to exact results (Supplementary Figure S1), Equations
 \eqref{ineqA} and \eqref{bistab_homozy_approx} offer reasonable, but imperfect approximations.

 \paragraph{Cost of driver in heterozygotes -- } 
When the fitness of drive heterozygotes is compromised ($s_h>0$), a self-promoting driver cannot invade when rare.
This results from the fact that,
when rare, 
$B$-bearing sperm and heterozygous eggs will rarely encounter one another ($\sim f_B^2$) but the allele still pays a
cost in heterozygous individuals ($\sim f_B$). 
However, this system too, is bistable -- as the driver increases in frequency it is more often fertilized by a driving sperm and therefore drives more effectively. 
Therefore, assuming HWE, if 
\begin{equation}
	s \lessapprox  d -1/2 +s_h(3-2d)/2
	\label{sForHetFix}
\end{equation}
this self-promoting driver deterministically fixes when its frequency is greater than
\begin{equation}
	f_B^* \approx \frac{a_1+\sqrt{a_1^2+8 s_h a_2}}{2 a_2}
	\label{thresh2}
\end{equation}
where, $a_1=1-2 ds_h+4 d s-2 d-3 s_h$ and $a_2=2(s-s_h)(2d-1)$.
Comparison of Equation \ref{thresh2} to exact results obtained by a
simple parameter search (Supplementary Figure S2)
show that this approximation is reasonably correct for small
parameter values; however, it underestimates $f_B^*$ for large parameter values, presumably because they result in strong departures from HWE.

@@

If the cost of drive is fully recessive (i.e. $s_h=0$), assuming HWE, 
	a rare paternal-genotype-dependent driver invades when 
	$s\lessapprox (d_{het}-1/2)/(d_{het})$, and when common, this driver fixes if 
	$s\lessapprox d_{hom}-1/2$, approximations well supported by exact results (Supplementary Figure S3).
Specifically, when drive in heterozygotes is large relative to that in homozygotes, 
	\begin{equation} d_{het}  \gtrapprox 1/(3-2d_{hom}) \label{polymale} \end{equation}
	fixation criteria are more stringent than invasion criteria, 
	and therefore some values of $s$ can maintain a stable polymorphism. 
Under these parameter values, a rare paternal-genotype-dependent driver 
	can increase in frequency because it gains a transmission advantage and suffers 
	no fitness cost when heterozygous eggs are fertilized by 
	$A$-bearing sperm of heterozygous males. 
As the frequency of the $B$ allele increases, 
	it will be unable to 
	avoid producing unfit homozygous offspring, leaving it trapped in
	the population at frequency $f_{B\text{ pat}}^*$. 
Assuming HWE, a recessive fitness cost ($h_s=0$), and dominance of driver ($d_{het}=d_{hom}$) this equilibrium frequency is
\begin{equation}f_{B\text{ pat}}^*\approx2 (1 + 2d_{hom}[s - 1])/([2 s - 1][2d_{hom}- 1]) \label{eqmale} \end{equation}
By contrast, when $d_{het} \lessapprox 1/(3-2d_{hom})$ the case is reversed, and the model is bistable.

@@

For all parameters sustaining a polymorphism at the drive locus ($s>d_0-1/2$), this corresponds to a decrease in frequency of the $C$ allele when it enhances drive ($\epsilon >0$ -- the $B^+$ model, above), 
	and an increase in frequency of the $C$ allele when it suppresses drive ($\epsilon <0$ -- the $B^-$ model, above). 
More generally, even when the cost of drive is not fully recessive, the $B^-$ allele will invade and fix under all parameters sustaining a previous polymorphism at the drive locus (see Mathematical Supplement).

 \subsubsection{Model 5. Drive-modifier in repulsion phase:}
When the $C$ allele is tightly linked to the non-driver, 
	genotypic fitnesses equal $w_{CC}=w_{AC}=w_{AA}=1$, and $w_{BC}=w_{AB}=1-s_h$. 
Assuming HWE, a recessive fitness cost to drive, and assuming that the $A/B$ locus is at its equilibrium frequency, the change in frequency of a rare drive modifier is
\begin{equation}
	\Delta C \approx -\epsilon f_{C^-}^2 \frac{ \left(2 d_0 s-\sqrt{2} \\ \sqrt{s (2 d_0 (d_0 (s-2)+2)-1)}\right)}{2\bar{w}s (2 d_0 -1) } \label{A-}
\end{equation}
For all values of interest ($0<s<1$, $0.5<d_0<1$), the change in frequency a rare $C$ allele is positive when it decreases drive (i.e. $\epsilon <0$, corresponding to the $A^-$ model, above), a result which holds qualitatively for a common $C$ allele, as well (Mathematical Supplement). 
Somewhat counterintuitively, the spread of the $A^-$ allele is substantially slower than that of the $B^-$ allele (it is on the order of $C^{2}$ rather than $C$). 
This is because the $A^-$ allele will never occur in drive-homozygotes and therefore only spreads by preventing itself from the cheating of the driver.

@@

\begin{acknowledgments} \end{acknowledgments}
\bibliography{refs}
\end{article}

>>>>

@@

It is therefore somewhat surprising that despite the intense evolutionary pressure on female meiosis to prevent meiotic drive, 
it is potentially open to sabotage by a virtual stranger -- a haploid sperm genome.
That is, in many animal species, female meiosis is completed only after fertilization \cite{Masui_book}, 
	creating ample opportunity for interaction between the sperm and
	female meiotic machinery (note that the alternation of generations in
	likely precludes this interaction in plants). 
Therefore, a `green-bearded' \cite{Gardner2010} sperm-acting allele that recognizes and facilitates the meiotic drive of a genetically equivalent allele in heterozygous females 
     could presumably rapidly spread through a population. 
At first sight, female meiosis appears primed for exploitation by such selfish systems.  
Why then is the requirement of fertilization to complete female meiosis so ubiquitous?

@@

\section{Results}
\subsection{Invasion of an allele that promotes its own drive}
In the standard single-locus, biallelic model of female meiotic drive,
the driving allele is transmitted to the egg in heterozygotes with
probability  $d > 1/2$, regardless of sperm genotype (e.g. \cite{Ubeda2004} and see Model 1 in the Appendix for more details). 
To depict a case of a self-promoting meiotic driver,  we modify this standard model such 
	that the driver is only effective when fertilized by a sperm carrying that allele (see Figure 1A and Model 2 	in the Appendix and Table S1). 
We then identify the conditions allowing for the spread of this self-promoting driver, 
	and evaluate whether a driver of this form could generate a sustained conflict favoring the evolution of suppressors. 
We conclude our single locus results with an analysis of a related model (Model 3) - in which
drivers influence their transmission in females via paternal genotype,
rather than sperm haplotype.

@@

When a self-promoting driver does spread, 
	it spends much time at low frequency, 
	because the paucity of complimentary sperm compromises its ability to drive. 
However, once relatively common, it  rapidly achieves fixation due to its
	positive frequency dependent behavior (Figure 1B.1).  
The positive frequency dependence of a self-promoting driver can also
	induce bistability in its spread -- some values of $s$ 
	allow the fixation of this driver when common, but 
	preclude its invasion when rare (Equation \ref{ineqA} and Figure 1B). 
In this case, the driver will be fixed if it reaches a frequency greater than some threshold 
	(approximated in Equation \ref{bistab_homozy_approx} and  presented exactly in 
	Figure S1), and lost otherwise. 
For most parameters, this threshold is likely too high to be reached by drift, 
	and therefore  the fate of self-promoting drivers is determined
	by the more restrictive invasion criteria rather than the fixation criteria.

@@

\subsection{Two locus models of sperm-dependent female drive}
Models 2 and 3, above, explored the dynamics of an allele that drove in females when signaled by a complementary signal in sperm.   
We complement this single-locus approach 
	with alternative models of two loci - one a female driver, 
	and the other, a sperm-acting allele which modifies the effect of drive upon fertilization. 
In this model, a female meiotic driver with no sperm-dependency 
	initially reaches drive-viability equilibrium (with two alleles
	$A$ and $B$ are the ancestral non-driver and driver alleles, Figure 2A1). 
Subsequently, a sperm-acting modifier of female meiotic drive arises at another locus.

@@

%%%sperm-acting facilitator
When the modifier of drive is tightly linked to the driver and
enhances drive (i.e. in coupling phase), 
	we label  this non-recombining drive/modifier haplotype as the $B^+$ allele.  
The $B^+$ allele acts in sperm to increase the effectiveness of drive for both
	the $B$ and  $B^{+}$ alleles in $AB$ and $AB^{+}$ heterozygotes (see Figure 2A2, and Model 4 in the Appendix and Table S1). 
Naively, $B^{+}$ may spread by capitalizing on the additional drive it causes; however,  
	this is not the case for a few simple reasons. 
First, the novel $B^{+}$ haplotype
	arises when the ancestral driver 
	is at drive-selection balance, 
	and therefore immediately suffers a homozygous fitness cost.  
Worse yet, a novel $B^{+}$ haplotype most often helps 
	the $B$  allele drive ($B^+$ sperm meeting $AB$ eggs), because $B$ is initially more common than $B^{+}$. 
Therefore, sperm-acting drive facilitator alleles experience a profound disadvantage 
	in this scenario, even more so than under the previous two allele model. 
We have found no parameter range of this
	three allele system that allows the sperm-acting drive facilitator $B^{+}$ to
	invade the population (Appendix Model 4, Equation \eqref{coupling}, and Appendix S1).

@@

\section{Appendix}
We highlight simple analytical results from: 
	the standard model of female meiotic drive (Model 1); a sperm-dependent 
	model of female meiotic drive (Model 2); a male-genotype-dependent model of
	female meiotic drive (Model 3); and more complex two-locus sperm-dependent drive models (Models 4-6). 
All models include a biallelic locus ($A/B$) with non-driving and driving alleles in frequencies $f_A$ and $f_B$, 
	respectively, while more complex models include more loci and/or alleles.  
Transmission rules describing the outcomes of all matings in each
	model are presented in Table S1. 
The fitness of genotype, $g$ is sex-independent and equals $1$, $1-h_s$, and $1-s$ for genotypes $AA$, $AB$, and $BB$, respectively. 
Genotypic frequencies  equal  $f_g$ for adults in the current generation, 
	$f_g'$ in the next generation of zygotes (i.e. after recombination, random mating, drive, and syngamy, but before selection)
	and $f_g''$ in adults after selection. 
After a complete generation $f_g'' = f_g' w_g/\bar{w}$, where $\bar{w}$ is the population mean fitness and equals $\Sigma w_g f_g'$. 
Because many of our analyses assume genotype frequencies expected under Hardy Weinberg Equilibrium (HWE), we note which analytical results are approximations. 
We verify these approximations with exact numerical iterations in Figures S1-S3 , and detail the derivation of these approximations in Appendix S1.

@@

\paragraph{Recessive fitness cost of self-promoting driver -- }
When fully recessive, the change in frequency of the self-promoting driver across generations equals 
\begin{equation}
\Delta f_B=\frac{f_A f_B^2}{\bar{w}} \left( \left(1-F\right)\left( d\left(1-2 f_A s\right) - f_B s-\frac{1}{2}\right) - s  F \right)
\label{deltadriver}
\end{equation}
where $F$ is the deviation from genotypic frequencies expected under Hardy-Weinberg. 
Assuming HWE  ($F=0$) a common, recessive, self-promoting driver invades if $s\lessapprox(2 d - 1)/(4 d)$, and fixes if
 $s\lessapprox(2d-1)/2$. 
 Therefore, when 
\begin{equation}
(2 d - 1)/(4 d)  \lessapprox  s  \lessapprox  (2d-1)/2\label{ineqA}
\end{equation} 
a recessive, self-promoting driver will deterministically fix if drift,
 	mutation, or migration pressure bring its frequency above
\begin{equation} 
f^*_{B\text{ recessive}} \approx (1-2d+4ds)/(2s(2d-1)) \label{bistab_homozy_approx}
\end{equation}
 but it will be lost when introduced below this frequency. 
 Compared to exact results (Figure S1), Equations
 \eqref{ineqA} and \eqref{bistab_homozy_approx} offer reasonable, but imperfect approximations.

 \paragraph{Cost of driver in heterozygotes -- } 
When the fitness of drive heterozygotes is compromised ($s_h>0$), a self-promoting driver cannot invade when rare.
This results from the fact that,
when rare, 
$B$-bearing sperm and heterozygous eggs will rarely encounter one another ($\sim f_B^2$) but the allele still pays a
cost in heterozygous individuals ($\sim f_B$). 
However, this system too, is bistable -- as the driver increases in frequency it is more often fertilized by a driving sperm and therefore drives more effectively. 
Therefore, assuming HWE, if 
\begin{equation}
	s \lessapprox  d -1/2 +s_h(3-2d)/2
	\label{sForHetFix}
\end{equation}
this self-promoting driver deterministically fixes when its frequency is greater than
\begin{equation}
	f_B^* \approx \frac{a_1+\sqrt{a_1^2+8 s_h a_2}}{2 a_2}
	\label{thresh2}
\end{equation}
where, $a_1=1-2 ds_h+4 d s-2 d-3 s_h$ and $a_2=2(s-s_h)(2d-1)$.
Comparison of Equation \ref{thresh2} to exact results obtained by a
simple parameter search (Figure S2)
show that this approximation is reasonably correct for small
parameter values; however, it underestimates $f_B^*$ for large parameter values, presumably because they result in strong departures from HWE.

@@

If the cost of drive is fully recessive (i.e. $s_h=0$), assuming HWE, 
	a rare paternal-genotype-dependent driver invades when 
	$s\lessapprox (d_{het}-1/2)/(d_{het})$, and when common, this driver fixes if 
	$s\lessapprox d_{hom}-1/2$, approximations well supported by exact results (Figure S3).
Specifically, when drive in heterozygotes is large relative to that in homozygotes, 
	\begin{equation} d_{het}  \gtrapprox 1/(3-2d_{hom}) \label{polymale} \end{equation}
	fixation criteria are more stringent than invasion criteria, 
	and therefore some values of $s$ can maintain a stable polymorphism. 
Under these parameter values, a rare paternal-genotype-dependent driver 
	can increase in frequency because it gains a transmission advantage and suffers 
	no fitness cost when heterozygous eggs are fertilized by 
	$A$-bearing sperm of heterozygous males. 
As the frequency of the $B$ allele increases, 
	it will be unable to 
	avoid producing unfit homozygous offspring, leaving it trapped in
	the population at frequency $f_{B\text{ pat}}^*$. 
Assuming HWE, a recessive fitness cost ($h_s=0$), and dominance of driver ($d_{het}=d_{hom}$) this equilibrium frequency is
\begin{equation}f_{B\text{ pat}}^*\approx2 (1 + 2d_{hom}[s - 1])/([2 s - 1][2d_{hom}- 1]) \label{eqmale} \end{equation}
By contrast, when $d_{het} \lessapprox 1/(3-2d_{hom})$ the case is reversed, and the model is bistable.

@@

For all parameters sustaining a polymorphism at the drive locus ($s>d_0-1/2$), this corresponds to a decrease in frequency of the $C$ allele when it enhances drive ($\epsilon >0$ -- the $B^+$ model, above), 
	and an increase in frequency of the $C$ allele when it suppresses drive ($\epsilon <0$ -- the $B^-$ model, above). 
More generally, even when the cost of drive is not fully recessive, the $B^-$ allele will invade and fix under all parameters sustaining a previous polymorphism at the drive locus (see Appendix S1).

 \subsubsection{Model 5. Drive-modifier in repulsion phase:}
When the $C$ allele is tightly linked to the non-driver, 
	genotypic fitnesses equal $w_{CC}=w_{AC}=w_{AA}=1$, and $w_{BC}=w_{AB}=1-s_h$. 
Assuming HWE, a recessive fitness cost to drive, and assuming that the $A/B$ locus is at its equilibrium frequency, the change in frequency of a rare drive modifier is
\begin{equation}
	\Delta C \approx -\epsilon f_{C^-}^2 \frac{ \left(2 d_0 s-\sqrt{2} \\ \sqrt{s (2 d_0 (d_0 (s-2)+2)-1)}\right)}{2\bar{w}s (2 d_0 -1) } \label{A-}
\end{equation}
For all values of interest ($0<s<1$, $0.5<d_0<1$), the change in frequency a rare $C$ allele is positive when it decreases drive (i.e. $\epsilon <0$, corresponding to the $A^-$ model, above), a result which holds qualitatively for a common $C$ allele, as well (Appendix S1). 
Somewhat counterintuitively, the spread of the $A^-$ allele is substantially slower than that of the $B^-$ allele (it is on the order of $C^{2}$ rather than $C$). 
This is because the $A^-$ allele will never occur in drive-homozygotes and therefore only spreads by preventing itself from the cheating of the driver.

@@

\begin{acknowledgments} \end{acknowledgments}
%\bibliography{refs}
\input{PNASSubmission.bbl}
\end{article}

\begin{figure*}
\includegraphics{selfprom.eps}
\caption{{\bf{A.}} A visual depiction of our model of `self-promoting' driver. 
	Transmission probabilities for alleles through female
 	 meiosis depend on sperm genotype. 
	 The non-driving $A$-allele, and self-promoting $B$-allele
	 are represented by unfilled and filled circles, respectively. 
	 {\bf{B.}} Evolution of a self-promoter and standard driver. 
	 	Assuming that the fitnesses of drive homozygotes and 
		heterozygotes are $1-s$ and $1$, respectively. 
	 	\emph{Main figure:} Boundary conditions for the invasion 
		and fixation of self-promoting and standard meiotic drivers, 
		with drive coefficient, $d$. Colored regions depict exact results, 
		while lines  represent analytical approximations. 
	 \emph{B1:}  Trajectories of sperm-dependent female drive
		 %alleles that can invade the population, 
		 each allele has $s =0.1$ against the
		 homozygotes.  The drive coefficient is denoted by color. 
 }   
\label{Eggsperm}
\end{figure*}

\begin{figure*}
	\includegraphics[width = .95
          \textwidth]{twolocus.pdf} 
\caption{Models of a sperm-acting drive modifier tightly linked to a meiotic driver. 
{\bf (A) } 
Sperm carrying the derived allele at the modifier locus (filled squares) alters transmission  
	at the driving allele (filled circles) during female meiosis.
        Alleles at these two tightly linked loci form three haplotypes (top of A). 	
	{\bf{A1)}} In the standard model of drive there is no
        variation at the modifier, 
	and the driver is transmitted to the egg with probability $d_0$. 
	{\bf{A2)}} The modifier allele increases the transmission of the drive allele ($d_1 > d_0$), and due to their shared genetic background, also increases its drive. 
	{\bf{A3 \& A4)}} The sperm-acting modifier acts to decrease
        drive  ($d_1=1/2$ in A3 \& A4, or more generally, $d_1 < d_0$) and arises on the same or opposite
        background from the driver (A3 \& A4 respectively). 
{\bf{(B)}} Invasion of a sperm-acting drive suppressor linked to a driver. 
	After the driver ($B$ haplotype) reaches drive selection equilibrium, we introduce a sperm acting drive modifier. 
	We assume full drive ($D_0 =1$), a recessive lethal fitness cost to drive ($h_s=0$, $s=1$) and that the sperm-acting modifier results in a fair meiosis. 
{\bf {B1)}} The $B^-$ allele replaces the ancestral drive haplotype, but segregates at a lower equilibrium frequency.
{\bf {B2)}} The $A^-$ allele replaces the ancestral non-driving haplotype, and in this case, removes the driver from the population. }
 \label{Eggsperm_3_allele_cartoon}
\end{figure*}
